---
title: 'Round 2: Retention data and customer intelligence'
author: "yuan WANG"
date: "11/14/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load library

```{r}
library(tidyverse)
#library(caret)
#library(randomForest)
library(pROC)
library(lightgbm)
```

## Read data

```{r}
t117 <- read_csv('Retention-Data-fixed/Retention-train_fixed.csv')
t120 <- read_csv('Retention-Data-fixed/Retention-score-fixed.csv')

glimpse(t117)
glimpse(t120) #miss promo and churnIn3Month
```


## Missing and unique values

```{r}
# train
t117 %>% 
  summarise_all( class ) %>%
  gather("Variable","Type") %>%
  bind_cols(
    t117 %>% 
      summarise_all( ~sum(is.na(.))/n() ) %>%
      gather("Variable","Missing") %>%
      select(Missing)
  ) %>%
  bind_cols(
    t117 %>% 
      summarise_all(n_distinct) %>%
      gather("Variable","numDistinct") %>%
      select(numDistinct)
  ) %>%
  print(n=100)
# test
t120 %>% 
  summarise_all( class ) %>%
  gather("Variable","Type") %>%
  bind_cols(
    t120 %>% 
      summarise_all( ~sum(is.na(.))/n() ) %>%
      gather("Variable","Missing") %>%
      select(Missing)
  ) %>%
  bind_cols(
    t120 %>% 
      summarise_all(n_distinct) %>%
      gather("Variable","numDistinct") %>%
      select(numDistinct)
  ) %>%
  print(n=100)


# Nearly all missing: timeSinceLastIsOverData,  minutesVoice, timeSinceLastIsOverVoice
# Moderate missing: timeSinceLastTechProb, timeSinceLastComplaints
# slight missing: phonePrice, cashDown, phoneBalance
```

## Deal with missing values

### timeSinceLastIsOverData

```{r}
temp_summary <- t117 %>%
  group_by(timeSinceLastIsOverData,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=100)

temp_summary %>%
  ggplot(aes(x=(timeSinceLastIsOverData),y=leave))+
  geom_bar(stat = "identity")

temp_summary %>% filter(is.na(timeSinceLastIsOverData))

# Removed, too many missing, hard to conclude if there is a pattern
```

### minutesVoice

```{r}
temp_summary <- t117 %>%
  group_by(minutesVoice,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=100)

temp_summary %>%
  ggplot(aes(x=as.character(minutesVoice),y=leave))+
  geom_bar(stat = "identity")

# Clients with missing minutesVoice has a much lower rate of leaving
# Marked, impute NA with 0,
# Create a new variable:
# zerominutesVoice = is.na(minutesVoice)

```

### timeSinceLastIsOverVoice

```{r}
temp_summary <- t117 %>%
  group_by(timeSinceLastIsOverVoice,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n()) %>%
  mutate(timeSinceLastIsOverVoice=as.integer(timeSinceLastIsOverVoice)) %>%
  arrange(timeSinceLastIsOverVoice)
temp_summary %>% print(n=100)

temp_summary %>%
  ggplot(aes(x=timeSinceLastIsOverVoice,y=leave))+
  geom_bar(stat = "identity")

temp_summary %>% filter(is.na(timeSinceLastIsOverVoice))

# Removed, too many missing, hard to conclude if there is a pattern
```


## timeSinceLastTechProb
```{r}
temp_summary <- t117 %>%
  group_by(timeSinceLastTechProb,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=timeSinceLastTechProb,y=leave))+
  geom_bar(stat = "identity")

temp_summary %>% filter(is.na(timeSinceLastTechProb))

# 0 has a significantly large rate of leaving, NA should be imputed differently 
# Marked, in feature engineering, create a binary variable, 
# noTechProb = 1 if timeSinceLastTechProb==0

```

## timeSinceLastComplaints
```{r}
temp_summary <- t117 %>%
  group_by(timeSinceLastComplaints,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=timeSinceLastComplaints,y=leave))+
  geom_bar(stat = "identity")

temp_summary %>% filter(is.na(timeSinceLastComplaints))

# 0 has a significantly large rate of leaving, NA should be imputed differently 
# The peak at 114 is 1, which is not reliable as there is only one client.
# Marked, in feature engineering, create a binary variable, 
# noComplaints = 1 if timeSinceLastComplaints==0

```

## phonePrice
```{r}
summary(t117$phonePrice)
summary(t120$phonePrice)
table(t117$planType)
table(t120$planType)

t117 %>% 
  ggplot(aes(x=phonePrice,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)



# NA is caused by the fact the clients brought their own phones
# Marked, leave NA there use model that can deal with NA automatically
# otherwise consider imputing NA by 0
```

## cashDown
```{r}
summary(t117$cashDown)
summary(t120$cashDown)
table(t117$planType)
table(t120$planType)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=cashDown))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=cashDown,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)


t117 %>%
  mutate(zeroCashDown= cashDown==0) %>%
  group_by(zeroCashDown) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())


# Marked, leave NA there as a seperate category, 
# use zeroCashDown instead for modeling
```

## phoneBalance
```{r}
summary(t117$phoneBalance)
summary(t120$phoneBalance)
summary(t117$cashDown)
summary(t120$cashDown)

# head(t117$phoneBalance+t117$cashDown)
# head(t117$phonePrice)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=phoneBalance))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=phoneBalance,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)


t117 %>%
  mutate(zerophoneBalance = phoneBalance==0) %>%
  group_by(zerophoneBalance) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())


# Marked, set NA as 0
```





## Further exploration

### Add familySize

```{r}
t117 <- t117 %>%
  group_by(IDfamily) %>%
  mutate(numFamily=n()) %>%
  ungroup()

t120 <- t120 %>%
  group_by(IDfamily) %>%
  mutate(numFamily=n()) %>%
  ungroup()

table(t117$numFamily)
table(t120$numFamily)

#
temp_summary <- t117 %>%
  group_by(numFamily,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n()) %>%
  mutate(prop=count/sum(count))
temp_summary %>% print(n=200)

# For two clients in the same family, will they quit together?
# No 
t117 %>%
  filter(numFamily==2) %>%
  group_by(IDfamily) %>%
  summarise(leave=mean(churnIn3Month)) %>%
  group_by(leave) %>%
  summarise(count=n())


# Marked, in feature engineering, make it a count variable
```

### nbAdultAvg               

```{r}
summary(t117$nbAdultAvg)
summary(t120$nbAdultAvg)


t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=nbAdultAvg))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=nbAdultAvg,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```


### chrono                       

```{r}
summary(t117$chrono)
summary(t120$chrono)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=chrono))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=chrono,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```


### age                       

```{r}
summary(t117$age)
summary(t120$age)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=age))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=age,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a count variable
```


### gender                   

```{r}
table(t117$gender)
table(t120$gender)

temp_summary <- t117 %>%
  group_by(gender,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)


# Marked, in feature engineering, create a factor.
# may be dropped as proportions are close
```

### isWorkPhone

```{r}
table(t117$isWorkPhone)
table(t120$isWorkPhone)

temp_summary <- t117 %>%
  group_by(isWorkPhone,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)


# Marked, in feature engineering, create a factor.
```


### planType

```{r}
table(t117$planType)
table(t120$planType)

temp_summary <- t117 %>%
  group_by(planType,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)


# Marked, in feature engineering, create a factor.
```


### data                     

```{r}
summary(t117$data)
summary(t120$data)

temp_summary <- t117 %>%
  group_by(data,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=data,y=leave))+
  geom_bar(stat = "identity")


# Marked, in feature engineering, make it a numerical variable
```


### dataAvgConsumption                     

```{r}
summary(t117$dataAvgConsumption)
summary(t120$dataAvgConsumption)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=dataAvgConsumption))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=dataAvgConsumption,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```



### nbrIsOverData                     

```{r}
summary(t117$nbrIsOverData)
summary(t120$nbrIsOverData)

temp_summary <- t117 %>%
  group_by(nbrIsOverData,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=nbrIsOverData,y=leave))+
  geom_bar(stat = "identity")

# Marked, in feature engineering, make a binary variable 
# IsOverData = 1 if nbrIsOverData>0
```



### unlimitedVoice

```{r}
table(t117$unlimitedVoice)
table(t120$unlimitedVoice)

temp_summary <- t117 %>%
  group_by(unlimitedVoice,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)


# Marked, in feature engineering, create a factor.
```

### voiceAvgConsumption                 

```{r}
summary(t117$voiceAvgConsumption)
summary(t120$voiceAvgConsumption)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=voiceAvgConsumption))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=voiceAvgConsumption,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```


### nbrIsOverVoice

```{r}
table(t117$nbrIsOverVoice)
table(t120$nbrIsOverVoice)

temp_summary <- t117 %>%
  group_by(nbrIsOverVoice,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=nbrIsOverVoice,y=leave))+
  geom_bar(stat = "identity")

# Removed. Too rare non-zero cases.
```


### unlimitedText

```{r}
table(t117$unlimitedText)
table(t120$unlimitedText)


# Removed. One category dominante the others.
```

### textoAvgConsumption                 

```{r}
summary(t117$textoAvgConsumption)
summary(t120$textoAvgConsumption)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=textoAvgConsumption))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=textoAvgConsumption,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```

### baseMonthlyRateForPlan

```{r}
table(t117$baseMonthlyRateForPlan)
table(t120$baseMonthlyRateForPlan)

temp_summary <- t117 %>%
  group_by(baseMonthlyRateForPlan,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=baseMonthlyRateForPlan,y=leave))+
  geom_bar(stat = "identity")

# Marked, in feature engineering, make it a numerical variable
```

### baseMonthlyRateForPhone

```{r}
summary(t117$baseMonthlyRateForPhone)
summary(t120$baseMonthlyRateForPhone)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=baseMonthlyRateForPhone))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=baseMonthlyRateForPhone,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```


### nbrTechnicalProblems

```{r}
table(t117$nbrTechnicalProblems)
table(t120$nbrTechnicalProblems)

temp_summary <- t117 %>%
  group_by(nbrTechnicalProblems,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=nbrTechnicalProblems,y=leave))+
  geom_bar(stat = "identity")

# Marked, in feature engineering, make it a numerical variable
```


### nbrComplaints

```{r}
table(t117$nbrComplaints)
table(t120$nbrComplaints)

temp_summary <- t117 %>%
  group_by(nbrComplaints,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

temp_summary %>%
  ggplot(aes(x=nbrComplaints,y=leave))+
  geom_bar(stat = "identity")

# Marked, in feature engineering, make it a numerical variable
```



### promo

```{r}
table(t117$promo)

temp_summary <- t117 %>%
  group_by(promo,.drop = FALSE) %>%
  summarise(leave=mean(churnIn3Month),
            count=n())
temp_summary %>% print(n=200)

# Marked
```


### lifeTime

```{r}
summary(t117$lifeTime)
summary(t120$lifeTime)

t117 %>% 
  ggplot(aes(x=factor(churnIn3Month),y=lifeTime))+
  geom_boxplot()

t117 %>% 
  ggplot(aes(x=lifeTime,y=stat(density), 
             fill=factor(churnIn3Month)))+
  stat_density(position='identity',alpha=0.5)

# Marked, in feature engineering, make it a numerical variable
```


### promo

```{r}
table(t117$churnIn3Month)
table(t117$churnIn3Month)/nrow(t117)

# Marked
```


## Feature engineering

```{r}
t117_preprocessed <- t117 %>%
  select(-timeSinceLastIsOverData,
         -timeSinceLastIsOverVoice,
         -nbrIsOverVoice,
         -unlimitedText) %>%
  group_by(IDfamily) %>%
  mutate(numFamily=n()) %>%
  ungroup() %>%
  mutate(noTechProb= addNA(factor(timeSinceLastTechProb==0)),
         noComplaints = addNA(factor(timeSinceLastComplaints==0)),
         zeroCashDown= addNA(factor(cashDown==0)),
         IsOverData = nbrIsOverData>0,
         zerominutesVoice = is.na(minutesVoice) ) %>%
  select(-timeSinceLastTechProb,
         -timeSinceLastComplaints,
         -cashDown,
         -nbrIsOverData,
         -minutesVoice) %>%
  mutate(phonePrice = replace_na(phonePrice,0),
         phoneBalance = replace_na(phoneBalance,0),
         gender = factor(gender),
         isWorkPhone = factor(isWorkPhone),
         planType = factor(planType),
         churnIn3Month=factor(churnIn3Month)) %>%
  select(-ID,
         -IDfamily)



t120_preprocessed <- t120 %>%
  select(-timeSinceLastIsOverData,
         -timeSinceLastIsOverVoice,
         -nbrIsOverVoice,
         -unlimitedText) %>%
  group_by(IDfamily) %>%
  mutate(numFamily=n()) %>%
  ungroup() %>%
  mutate(noTechProb= addNA(factor(timeSinceLastTechProb==0)),
         noComplaints = addNA(factor(timeSinceLastComplaints==0)),
         zeroCashDown= addNA(factor(cashDown==0)),
         IsOverData = nbrIsOverData>0,
         zerominutesVoice = is.na(minutesVoice) ) %>%
  select(-timeSinceLastTechProb,
         -timeSinceLastComplaints,
         -cashDown,
         -nbrIsOverData,
         -minutesVoice) %>%
  mutate(phonePrice = replace_na(phonePrice,0),
         phoneBalance = replace_na(phoneBalance,0),
         gender = factor(gender),
         isWorkPhone = factor(isWorkPhone),
         planType = factor(planType)) %>%
  select(-ID,
         -IDfamily)

```

```{r}
# Check
# Summary of the preprocessed data
t117_preprocessed %>% 
  summarise_all( class ) %>%
  gather("Variable","Type") %>%
  bind_cols(
    t117_preprocessed %>% 
      summarise_all( ~sum(is.na(.))/n() ) %>%
      gather("Variable","Missing") %>%
      select(Missing)
  ) %>%
  bind_cols(
    t117_preprocessed %>% 
      summarise_all(n_distinct) %>%
      gather("Variable","numDistinct") %>%
      select(numDistinct)
  ) %>%
  print(n=100)


t120_preprocessed %>% 
  summarise_all( class ) %>%
  gather("Variable","Type") %>%
  bind_cols(
    t120_preprocessed %>% 
      summarise_all( ~sum(is.na(.))/n() ) %>%
      gather("Variable","Missing") %>%
      select(Missing)
  ) %>%
  bind_cols(
    t120_preprocessed %>% 
      summarise_all(n_distinct) %>%
      gather("Variable","numDistinct") %>%
      select(numDistinct)
  ) %>%
  print(n=100)
```


## Start modeling

### Create 5-fold cross validation

```{r}
set.seed(65234897)
cvFold <- sample(1:5,nrow(t117_preprocessed), replace = TRUE)
```

### logistic regression
```{r} 
# Logistic regression using cross-validation
# Used as baseline method
logistic1_fit <- vector("list",5)
auc_logistic <- numeric(5)
for(k in 1:5){
  cat(k,",")
  trainRDCI <- t117_preprocessed[cvFold!=k,]
  validRDCI <- t117_preprocessed[cvFold==k,]
  logistic1_fit[[k]] <- glm(churnIn3Month~.,
                              data=trainRDCI,
                              family=binomial())
  #summary(logistic1_fit[[k]])
  pred_logistic1 <- predict(logistic1_fit[[k]],
                                  newdata=validRDCI, 
                                  type="response")
  
  auc_logistic[k] <- roc(validRDCI$churnIn3Month,pred_logistic1,col="blue")$auc
}
auc_logistic
```

### lightgbm
```{r}

#lgb.unloader(wipe=TRUE)
set.seed(123)
catSet <- c("promo", 
            "gender", "isWorkPhone", 
            "planType", "noTechProb", 
            "noComplaints", "zeroCashDown")



lgb_list <- vector("list",5)
auc_lgb <- numeric(5)
params = list(objective = "binary",
              metric = "auc",
              num_iterations=1000,
              learning_rate=0.05,
              num_leaves= 55,
              min_child_samples= 500,
              max_bin= 55,
              max_depth=3,
              subsample= 0.8,  
              subsample_freq= 1,
              colsample_bytree= 0.8,  
              min_child_weight= 0,
              min_split_gain= 0.00001,
              #  lambda_l2=0.1,
              boosting="gbdt") #

for(k in 1:5){
  cat(k,",")
  trainRDCI <- t117_preprocessed[cvFold!=k,]  %>%
    mutate_if(is.factor, ~as.integer(.)) %>%
    select(-churnIn3Month) %>%
    mutate(promo=as.integer(promo))%>%
    as.matrix()
  
  validRDCI <- t117_preprocessed[cvFold==k,] %>%
    mutate_if(is.factor, ~as.integer(.)) %>%
    select(-churnIn3Month) %>%
    mutate(promo=as.integer(promo)) %>%
    as.matrix()
  
  trainLabel <- as.numeric(t117_preprocessed[cvFold!=k,]$churnIn3Month)-1
  validLabel <- as.numeric(t117_preprocessed[cvFold==k,]$churnIn3Month)-1
  
  # Creating the 'train' for modeling
  trainS = lgb.Dataset(data = trainRDCI,
                       label = trainLabel,
                       categorical_feature = catSet)
  
  # Creating the 'validation' for modeling
  valS = lgb.Dataset(data = validRDCI,
                     label = validLabel, 
                     categorical_feature = catSet)
  invisible(gc())
  
  # train lgb
  fit_lgb <- lgb.train(params, trainS, valids = list(validation = valS), 
                       nthread = 4,
                       verbose= -1, record=TRUE,
                       eval_freq = 10, early_stopping_rounds = 50)
  fit_lgb$best_iter <- which.max(unlist(fit_lgb$record_evals$validation$auc$eval))
  #fit_lgb$best_iter 
  auc_lgb[k] <- max(unlist(fit_lgb$record_evals$validation$auc$eval))
  
  # Feature importance
  # impBooster <- lgb.importance(fit_lgb, percentage = TRUE)
  # impBooster[,2:4] <- round(impBooster[,2:4],5)
  # impBooster
  
  
  lgb_list[[k]] <- fit_lgb
}

auc_lgb
```

### Comparison between logistic regression and lightgbm

```{r}
# Prefer lgb
cbind(auc_logistic,auc_lgb)
```


### Predict uplift 
```{r}
testRDCI_nopromo <- t120_preprocessed %>%
  mutate_if(is.factor, ~as.integer(.)) %>%
  # select(-churnIn3Month) %>%
  mutate(promo=as.integer(0))%>%
  as.matrix()
testRDCI_nopromo <- testRDCI_nopromo[,c(1:17,25,18:24)] #reorder to match the training order

testRDCI_promo <- t120_preprocessed %>%
  mutate_if(is.factor, ~as.integer(.)) %>%
  # select(-churnIn3Month) %>%
  mutate(promo=as.integer(1))%>%
  as.matrix()
testRDCI_promo <- testRDCI_promo[,c(1:17,25,18:24)]

preds_nopromo <- 0
preds_promo <- 0
for(k in 1:5){
  cat(k,"")
  preds_nopromo <- preds_nopromo + predict(lgb_list[[k]], 
                                         data = testRDCI_nopromo, 
                                         n = lgb_list[[k]]$best_iter )
  preds_promo <- preds_promo +predict(lgb_list[[k]], 
                                        data = testRDCI_promo, 
                                        n = lgb_list[[k]]$best_iter )
}
preds_nopromo <- preds_nopromo/5
preds_promo <- preds_promo/5

# Since churnIn3Month = 1 if Client has left in a 3-month window
# the we compute uplift using 
uplift <- preds_nopromo - preds_promo
summary(uplift)
plot(preds_nopromo,uplift)


```

### Expected profit for each client in the test set
```{r}
monthfee <- t120_preprocessed$baseMonthlyRateForPlan

profit_nopromo <- 0
for(k in 1:7){
  profit_nopromo <- profit_nopromo + dnbinom(k, 1, preds_nopromo)*monthfee*3*k/2
}
profit_nopromo <- (1-pnbinom(7, 1, preds_nopromo)) * monthfee *3 * 8/2
summary(profit_nopromo)

profit_promo <- 0
for(k in 1:7){
  profit_promo <- profit_promo + dnbinom(k, 1, preds_promo)*monthfee*3*k/2
}
profit_promo <- (1-pnbinom(7, 1, preds_promo)) * monthfee *3 * 8/2
summary(profit_promo)


# Compute profit_uplift
profit_uplift <- profit_promo-profit_nopromo
summary(profit_uplift)

profit_uplift_tab <- tibble(ID=t120$ID, IDfamily=t120$IDfamily, profit_uplift=profit_uplift)
write_csv(profit_uplift_tab, path = "profit_uplift_tab.csv")

# Compute profit_uplift for each familyID
profit_uplift_tab_family <- profit_uplift_tab %>%
  group_by(IDfamily) %>%
  summarize(average_profit_uplift= mean(profit_uplift),
            numFamily=n()) %>%
  arrange(desc(average_profit_uplift)) %>%
  mutate(cumNum=cumsum(numFamily))

write_csv(profit_uplift_tab_family, path = "profit_uplift_tab_family.csv")
```

### Use the expected profit uplift to find desired clients

```{r}
# Find the last family that has average_profit_uplift>10
lastIdx <- which(profit_uplift_tab_family$average_profit_uplift>10)
lastIdx <- lastIdx[length(lastIdx)]
lastIdx # 332762 families
profit_uplift_tab_family$cumNum[lastIdx] #need 373319 clients

# Compute the overall profit
overall_profit_uplift <- function(Nfamily){
  with(profit_uplift_tab_family[1:Nfamily,],
     sum((average_profit_uplift-10)*numFamily)- 10000* (cumNum[Nfamily]%/%5000) )
}




xnum <- c(seq(1000,325000,1000), 332762, seq(350000,500000,2500))
ynum <- sapply(xnum,overall_profit_uplift)
plot(xnum, ynum)

xnum[which.max(ynum)] #307000

profit_uplift_tab_family$cumNum[307000] #344415
10000* (profit_uplift_tab_family$cumNum[307000]%/%5000)
profit_uplift_tab_family$average_profit_uplift[307000]

# Output the first 307000 IDfamily 
output_IDfamily <- profit_uplift_tab_family[1:xnum[which.max(ynum)],] %>% select(IDfamily)
output_IDfamily


write_csv(output_IDfamily,"output_IDfamily1.csv") 

```


